Tidy data structure to support exploration and modeling of temporal data

### 2018-11-28 main.Rmd
added "data first" subsection

This paper proposes a unified data representation of temporal-context data, blending time series of nested and crossed factors into a two-dimensional column-homogeneous array in a long format. By leveraging the "tidy data" principles, observations and variables position and bridge their meanings in both physical and internal structures. Data manipulation involves in transforming either observations or variables, or both, which can be described and achieved with a collection of shorthand operators. A chain of data transformations lend itself to a data pipeline.

@@

# Software structure

data first, function starts with the first argument "data", chained with `%>%`. print display.

* Extensibility

>>>>

@@

# Software structure and design decisions

The **tsibble** package highly features modularity and extensibility.

The prime force that drives the software's design choices is "data". All functions in **tsibble** starts with `data` or its variants as the first argument, namely "data first". They work naturally with the pipe operator `%>%`, read as "then". This not only lays out a consistent interface but also addresses the significance of the data throughout the software.

Beyond the tools, the print display provides a quick and comprehensive glimpse of data in temporal context, particularly useful when handling a large collection of data. Below conveys the pieces of critical and contextual information about the data in Table \ref{tab:tb-sub}: (1) data dimension with its shorthand time interval, alongside time zone if date-times; (2) variables that constitute of the "key" with the number of series. These details aid users in understanding their data better and manipulate the data with care.

```{r tb-print}
```

## Modularity

## Extensibility
